Enabling conditions for effective community-based marine reserves in small-scale fisheries

### 2018-03-22 docs/paper/Villasenor-Derbez.Rmd
deleted old test html reg table

```{r load_data}
fish <- read.csv(here::here("data", "fish_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  filter(Comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(RC),
         RC %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(RC %in% c("El Faro - El Faro (Control)") & Ano == 2012)) %>% 
  mutate(GeneroEspecie = case_when(
    GeneroEspecie == "Cephalopholis cruentatus" ~ "Cephalopholis cruentata",
    GeneroEspecie == "Haemulon macrostomun" ~ "Haemulon macrostomum",
    GeneroEspecie == "Xcochin spp" ~ "Balistes capriscus",
    GeneroEspecie == "Pterois volitans/miles" ~ "Pterois volitans",
    GeneroEspecie == "Mycteroperca spp" ~ "Mycteroperca",
    GeneroEspecie == "Chromis spp" ~ "Chromis",
    GeneroEspecie == "Damisela spp" ~ "Stegastes",
    GeneroEspecie == "Haemulon spp" ~ "Haemulon",
    GeneroEspecie == "Lancero spp" ~ "Acanthurus",
    GeneroEspecie == "Kyphosus sectatrix/incisor" ~ "Kyphosus",
    GeneroEspecie == "Sebastes spp" ~ "Sebastes",
    GeneroEspecie == "Loro spp" ~ "Scarus",
    GeneroEspecie == "Lutjanus spp" ~ "Lutjanus",
    GeneroEspecie == "Mariposa spp" ~ "Chaetodon",
    GeneroEspecie == "Pluma spp" ~ "Calamus pennatula",
    GeneroEspecie == "Sparisoma aurolineatum" ~ "Sparisoma aurofrenatum",
    GeneroEspecie == "Vieja spp" ~ "Bodianus rufus",
    TRUE ~ GeneroEspecie
  ))

invert <- read.csv(here::here("data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  filter(Comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(RC),
         RC %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(RC %in% c("El Faro - El Faro (Control)") & Ano == 2012))

load(here::here("data","conapesca_2000-2015.RData"))

cpi <- read.csv(here::here("data", "CPI.csv"), stringsAsFactors = F, strip.white = T)

cpi_2014 <- cpi$CPI[cpi$Ano == 2014]

conapesca %<>%
  filter(UnidadEconomica %in% c("Scpp cozumel scl",
                                "Scpp jose maria azcorra scl",
                                "Scpp buzos y pescadores de la baja california scl")) %>% 
  filter(NombreComun %in% c("Langosta roja ent. fca.", "Langosta ent. fca.")) %>%
  group_by(UnidadEconomica, Ano, NombreComun) %>%
  summarize(PesoDesembarcado = sum(PesoDesembarcado), 
            PesoVivo = sum(PesoVivo),
            Valor = sum(Valor)) %>%
  filter(!(UnidadEconomica == "Scpp buzos y pescadores de la baja california scl" & NombreComun == "Langosta ent. fca.")) %>% 
  left_join(cpi, by = "Ano") %>% 
  mutate(Valor = Valor * (CPI / cpi_2014))

@@

```{r}
inv_summary <- group_by(invert, Comunidad, RC, Zona, Sitio, Transecto, Ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(Comunidad, RC, Zona) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  spread(Zona, n) %>% 
  select(Comunidad, RC, Control, Reserve = Reserva)

group_by(fish, Comunidad, RC, Zona, Sitio, Transecto, Ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(Comunidad, RC, Zona) %>% 
  summarize(Start = min(Ano), n = n()) %>% 
  ungroup() %>% 
  spread(Zona, n) %>% 
  mutate(Implementation = c(2006, 2012, 2013, 2013)) %>% 
  select(Comunidad, RC, Implementation, Start, Control, Reserve = Reserva) %>% 
  left_join(inv_summary, by = c("Comunidad", "RC")) %>% 
  knitr::kable(format = "latex",
               caption = "\\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.",
               col.names = c("Community", "Reserve - Control", "Imp", "Start", "Cf", "Rf", "Ci", "Ri"))
```

@@

```{r, prepare_covars}
fish_covars <- fish %>% 
  group_by(RC, Ano, Sitio, Zona, Transecto, Comunidad) %>% 
  count() %>% 
  select(-n)

invert_covars <- invert %>% 
  group_by(RC, Ano, Sitio, Zona, Transecto, Comunidad) %>% 
  count() %>% 
  select(-n)
```

```{r complete_fish}
fish_complete <- fish %>% 
  select(Ano, Sitio, Zona, Transecto, GeneroEspecie, Abundancia) %>% 
  group_by(Ano, Sitio, Zona, Transecto, GeneroEspecie) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  ungroup() %>% 
  complete(Ano, Transecto, nesting(Sitio, Zona, GeneroEspecie), fill = list(Abundancia = 0L)) %>% 
  left_join(fish_covars, by = c("Ano", "Sitio", "Zona", "Transecto")) %>% 
  select(Comunidad, Ano, RC, Sitio, Zona, Transecto, GeneroEspecie, Abundancia) %>% 
  arrange() %>% 
  filter(!is.na(RC))

species_bio <- MPAtools::species_bio

spp <- group_by(fish_complete, GeneroEspecie) %>% 
  count() %>% 
  left_join(species_bio, by = "GeneroEspecie") %>% 
  filter(is.na(a) | is.na(b))

FB_update <- rfishbase::length_weight(c("Kyphosus incisor", "Kyphosus sectatrix", "Pterois volitans", "Scarus guacamaia", "Chaetodon capistratus", "Chaetodon capistratus", "Chaetodon striatus", "Calamus pennatula"), fields = c("a", "b")) %>% 
  select(GeneroEspecie = sciname, a, b) %>% 
  mutate(GeneroEspecie = case_when(
    GeneroEspecie %in% c("Kyphosus sectatrix", "Kyphosus incisor") ~ "Kyphosus",
    GeneroEspecie %in% c("Chaetodon capistratus", "Chaetodon striatus") ~ "Chaetodon",
    TRUE ~ GeneroEspecie
  )) %>% 
  group_by(GeneroEspecie) %>% 
  summarize_all(mean, na.rm = T)

GenusLevelBio <- species_bio %>% 
  filter(Genus %in% c("Mycteroperca", "Chromis", "Stegastes", "Haemulon", "Acanthurus", "Sebastes", "Lutjanus", "Scarus")) %>%
  select(GeneroEspecie = Genus, a, b) %>% 
  group_by(GeneroEspecie) %>% 
  summarize_all(mean, na.rm = T)

species_bio %<>%
  select(GeneroEspecie, a, b) %>% 
  rbind(FB_update) %>% 
  rbind(GenusLevelBio)
```

```{r complete_inverts}
invert_complete <- invert %>%
  select(Ano, Sitio, Zona, Transecto, GeneroEspecie, Abundancia) %>% 
  group_by(Ano, Sitio, Zona, Transecto, GeneroEspecie) %>% 
  summarize(Abundancia = sum(Abundancia)) %>% 
  ungroup() %>% 
  complete(Ano, Transecto, nesting(Sitio, Zona, GeneroEspecie), fill = list(Abundancia = 0L)) %>% 
  left_join(fish_covars, by = c("Ano", "Sitio", "Zona", "Transecto")) %>% 
  select(Comunidad, Ano, RC, Sitio, Zona, Transecto, GeneroEspecie, Abundancia) %>% 
  arrange()
```

```{r model_fit}

# Invertebrates

## Lobsters
L_IN <- invert_complete %>%
  filter(GeneroEspecie == "Panulirus interruptus") %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F, spfe = F, family = "quasipoisson")

L_ME <- invert_complete %>% 
  filter(GeneroEspecie == "Panulirus argus") %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F, spfe = F, family = "quasipoisson")

L_PH <- invert_complete %>% 
  filter(GeneroEspecie == "Panulirus argus") %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F, spfe = F, family = "quasipoisson")

## Abundance
Ni_IN <- invert_complete %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F, family = "quasipoisson")

Ni_ME <- invert_complete %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F, family = "quasipoisson")

Ni_PH <- invert_complete %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F, family = "quasipoisson")

@@

## Abundance
N_IN <- fish_complete %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F, family = "quasipoisson")

N_ME <- fish_complete %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F, family = "quasipoisson")

N_PH <- fish_complete %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F, family = "quasipoisson")

>>>>

```{r load_data}
invert <- read.csv(file = here::here("data", "invertebrates.csv"))

fish <- read.csv(file = here::here("data", "fish.csv"))

conapesca <- read.csv(x = conapesca, file = here::here("data", "conapesca.csv"))

@@

```{r}
inv_summary <- group_by(invert, comunidad, rc, zona, sitio, transecto, ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, rc, zona) %>% 
  summarize(n = n()) %>% 
  ungroup() %>% 
  spread(zona, n) %>% 
  select(comunidad, rc, control = Control, reserve = Reserva)

group_by(fish, comunidad, rc, zona, sitio, transecto, ano) %>%
  count() %>% 
  ungroup() %>% 
  group_by(comunidad, rc, zona) %>% 
  summarize(ano = min(ano), n = n()) %>% 
  ungroup() %>% 
  spread(zona, n) %>% 
  mutate(implementation = c(2006, 2012, 2013, 2013)) %>% 
  select(comunidad, implementation, ano, rc, control = Control, reserve = Reserva) %>% 
  left_join(inv_summary, by = c("comunidad", "rc")) %>% 
  knitr::kable(format = "latex",
               caption = "\\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.",
               col.names = c("Community", "Reserve - Control", "Imp", "Start", "Cf", "Rf", "Ci", "Ri"))
```

@@

```{r model_fit}
# Invertebrates

## Lobsters
L_IN <- invert %>%
  filter(generoespecie == "Panulirus interruptus") %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F, spfe = F)

L_ME <- invert %>% 
  filter(generoespecie == "Panulirus argus") %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F, spfe = F)

L_PH <- invert %>% 
  filter(generoespecie == "Panulirus argus") %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F, spfe = F)

## Abundance
Ni_IN <- invert %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F)

Ni_ME <- invert %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F)

Ni_PH <- invert %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F)

@@

## Abundance
N_IN <- fish %>% 
  abundance(com = "Isla Natividad") %>% 
  model(sfe = F)

N_ME <- fish %>% 
  abundance(com = "Maria Elena") %>% 
  model(sfe = F)

N_PH <- fish %>% 
  abundance(com = "Punta Herrero") %>% 
  model(sfe = F)
